Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-09 main.tex
remove ctc todo, add no more information
small fixes/updates

\subsection{Connectionist Temporal Classification}
We use a \gls{CTC} model for our experiments.
It follows the setup described for the \gls{CTC} model in \cite{zhou2022efficient}.
\TODO{Add more description of the CTC model.}
All models are trained in a purely supervised fashion using the \gls{CTC} objective unless explicitly stated otherwise.
The official LibriSpeech 4-gram \gls{LM} is used and integrated using shallow fusion \cite{gulcehre2015shallow} during decoding.

@@

The proposed \fe in \cite{asapp2022performance} uses increasing inner dimensions and we use this approach in the last three lines of \refTab{table:features_w2v_size}.
The first layer uses a dimension of 64/128 and it is doubled after each layer with an odd index.
Additionally, we add point-wise convolutional layers after all but the first layer using the same inner dimension as the preceding layer for the last row of the table.
It can be observed that these configurations perform similarly to the 6 layer 512-dim baseline while reducing the training time by about 21\%, 19\% and 14\%, respectively.

>>>>

\subsection{Connectionist Temporal Classification}
We use a \gls{CTC} model for our experiments.
It follows the setup described for the \gls{CTC} model in \cite{zhou2022efficient}.
All models are trained in a purely supervised fashion using the \gls{CTC} objective unless explicitly stated otherwise.
The official LibriSpeech 4-gram \gls{LM} is used and integrated using shallow fusion \cite{gulcehre2015shallow} during decoding.

@@

The proposed \fe in \cite{asapp2022performance} uses increasing inner dimensions and we use this approach in the last three lines of \refTab{table:features_w2v_size}.
The first layer uses a dimension of 64/128 and it is doubled after each layer with an odd index.
Additionally, we add point-wise convolutional layers after all but the first layer using the same inner dimension as the preceding layer for the last row of the table.
It can be observed that these configurations perform similarly to the 6 layer 512-dim baseline while reducing the training time by about 21\%, 19\% and 14\%, respectively.
Note that the \gls{SC} features perform similar to the variant with dimension 64-512 while again around 10\% shorter training time.

### 2023-03-09 tables/features_pretraining.tex
small fixes/updates

\centering
\caption{Effect of pre-training the wav2vec 2.0 feature extractor using the unsupervised loss on the same data (LibriSpeech 960h).}
\label{table:features_pretraining}
\begin{tabular}{|c|c|S|c|S|c|}
\hline
\multicolumn{2}{|c|}{Feature Extractor} & \multicolumn{4}{c|}{{WER [\%]}} \\\cline{3-6}
                 \multicolumn{2}{|c|}{} &      \multicolumn{2}{c|}{{dev}} & \multicolumn{2}{c|}{{test}} \\\hline
                              Trainable & Pretrained &                         {clean} & other &                     {clean} & other \\\hline\hline
                                    yes &         no &                             2.9 &   6.8 &                             &   7.5 \\\cline{2-6}
                                        &        yes &                             2.9 &   6.9 &                             &   7.5 \\\cline{1-1}\cline{3-6}
                                     no &            &                             3.0 &   7.1 &                             &   7.8 \\
\hline
\end{tabular}

>>>>

\centering
\caption{Effect of pre-training the wav2vec 2.0 feature extractor using the unsupervised loss on the same data (LibriSpeech 960h).}
\label{table:features_pretraining}
\begin{tabular}{|c|c|S|c|S|c|}
\hline
\multicolumn{2}{|c|}{Feature Extractor} & \multicolumn{4}{c|}{{WER [\%]}} \\\cline{3-6}
                 \multicolumn{2}{|c|}{} &      \multicolumn{2}{c|}{{dev}} & \multicolumn{2}{c|}{{test}} \\\hline
                              Trainable & Pre-trained &                         {clean} & other &                     {clean} & other \\\hline\hline
                                    yes &          no &                             2.9 &   6.8 &                         3.3 &   7.5 \\\cline{2-6}
                                        &         yes &                             2.9 &   6.9 &                         3.3 &   7.5 \\\cline{1-1}\cline{3-6}
                                     no &             &                             3.0 &   7.1 &                         3.3 &   7.8 \\
\hline
\end{tabular}
